Constructing hierarchies

### 2023-10-02 analysis.Rmd
update

```{r, include=FALSE, echo=FALSE}
S <- rbind(c(1,1,1), c(0, 1, 1), diag(3))

@@

```{r, echo=FALSE, message=FALSE}
source("R/reconciliation.R")
library(forecast)
step2 <- function(Wb) {

  errors <- MASS::mvrnorm(1000, rep(0, 3), Wb)

  AR <- diag(c(0, 0.3, 0.4))
  series <- matrix(0, 1001, 3)
  for (i in 2:1001) {
    series[i,] <- AR %*% series[i-1, ] + errors[i-1,]
  }
  series <- series[102:1001,]
  series[,1] <- seq(from=1, to=5, length = 900) + series[,1]
  series[,2] <- seq(from=1, to=5, length = 900) + series[,2]

  plot_series <- ts(series)
  colnames(series) <- c("C", "D", "E")
  plot(plot_series)

  S2 <- S
  S2[2,] <- c(1, 1, 0)

  series2 <- series %*% t(S2)
  series <- series %*% t(S)
  # Cross Validation
  init_window <- 800
  step <- 10

  mat2list <- function(x){
    r <- lapply(seq_len(ncol(x)), function(i) unname(x[,i]))
    names(r) <- colnames(x)
    r
  } 
  accs <- vector("list", 3)
  names(accs) <- c("base", "mint", "mint2")
  for (i in 1:10) {
    train <- series[1:(790+10*i),]
    test <- series[(791+10*i):(800+10*i),]

    fcasts <- lapply(iterators::iter(train, by="col"), function(s){
      mdl <- forecast(auto.arima(s, seasonal = FALSE), h=10)
      list(resid = as.numeric(residuals(mdl)), fcasts = as.numeric(mdl$mean))
    })

    resids <- do.call(cbind, lapply(fcasts, function(x){
      x$resid
    }))
    fcasts <- do.call(cbind, lapply(fcasts, function(x){
      x$fcasts
    }))

    fcasts_B2 <- forecast(auto.arima(series2[1:(790+10*i), 2], seasonal = FALSE), h=10)
    resids2 <- resids
    resids2[,2] <- as.numeric(residuals(fcasts_B2))
    fcasts2 <- fcasts
    fcasts2[,2] <- as.numeric(fcasts_B2$mean)

    reconf <- reconcile.mint(S, fcasts, resids)
    reconf2 <- reconcile.mint(S2, fcasts2, resids2)

    rmse <- function(x, y) { 
      r <- sapply(c(1, 3, 4, 5), function(i){
        sqrt(mean((x[,i]-y[,i])^2))
      })
      names(r) <- c("A", "C", "D", "E")
      r
    }
    accs$base <- rbind(accs$base, rmse(fcasts, test))
    accs$mint <- rbind(accs$mint, rmse(reconf, test))
    accs$mint2 <- rbind(accs$mint2, rmse(reconf2, test))
  }
  accs$base <- mat2list(accs$base)
  accs$mint <- mat2list(accs$mint)
  accs$mint2 <- mat2list(accs$mint2)
  as_tibble(accs) %>% mutate(names = c("A", "C", "D", "E")) %>% tidyr::unnest(cols = c("base", "mint", "mint2"))
}
```

@@

$$
\begin{bmatrix}
y_{C,t} \\ y_{D,t} \\ y_{E,t}
\end{bmatrix} = \begin{bmatrix}0.0055 \\ 0.0055 \\ 0\end{bmatrix}t + \begin{bmatrix}
0 & 0 & 0 \\
0 & 0.3 & 0 \\
0 & 0 & 0.4
\end{bmatrix} \begin{bmatrix}
y_{C,t-1} \\ y_{D,t-1} \\ y_{E,t-1}
\end{bmatrix} + \begin{bmatrix}
e_{C,t} \\ e_{D,t} \\ e_{E,t}
\end{bmatrix}
$$

$\boldsymbol{e}_t$ has the following covariance matrix

$$
\begin{bmatrix}
1 & 0 & 0 \\
0 & 1 & x \\
0 & x & 1 \\
\end{bmatrix}
$$

### x=0.9

```{r, message=FALSE, echo=FALSE}
W <- diag(3)
W[2,3] <- 0.9
W[3,2] <- 0.9
r1 <- step2(W)
r1 %>% group_by(names) %>% summarise_all(mean)
```

### x=-0.9

```{r, message=FALSE, echo=FALSE}
W <- diag(3)
W[2,3] <- -0.9
W[3,2] <- -0.9
r1 <- step2(W)
r1 %>% group_by(names) %>% summarise_all(mean)
```

@@

```{r}
# representator rank
representator_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(representator, values, rank)) %>%
  mutate_at("values", purrr::map, function(x){
    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
      t() %>% colMeans()
    x %>% select(-values) %>%
      pivot_wider(names_from = "representator", values_from = "rank")
  }) %>%
  unnest("values")

representators <- c("error", "ts", "error.features", "ts.features", "forecast")

## in most cases, error is the best
representator_summarise %>% rowwise() %>%
  mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
  pull(min) %>%
  table()

## only in one case, error is the worst
representator_summarise %>% rowwise() %>%
  mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
  pull(max) %>%
  table()
mcb(representator_summarise %>% select(representators))

@@

### cluster rank
```{r}
# cluster rank
cluster_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(cluster, values, rank)) %>%
  mutate_at("values", purrr::map, function(x){
    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
      t() %>% colMeans() %>% rank()
    x %>% select(-values) %>%
      pivot_wider(names_from = "cluster", values_from = "rank")
  }) %>%
  unnest("values")

cluster_summarise %>% select(-c(representator, distance)) %>%
  mcb()

@@

```{r}
distance_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(distance, values, rank)) %>%
  mutate_at("values", purrr::map, function(x){
    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
      t() %>% colMeans() %>% rank()
    x %>% select(-values) %>%
      pivot_wider(names_from = "distance", values_from = "rank")
  }) %>%
  unnest("values")
distance_summarise %>% select(-c(representator, cluster)) %>%
  mcb()

distances <- c("euclidean", "dtw", "negcor", "cor", "uncorrelation")
distance_summarise %>% rowwise() %>%
  mutate(max = distances[which.max(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
  pull(max) %>%
  table()
distance_summarise %>% rowwise() %>%
  mutate(min = distances[which.min(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
  pull(min) %>%
  table()
```

@@

```{r, message=FALSE}
# representator rank
representator_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(representator, values, rank)) %>%
  mutate_at("values", purrr::map, function(x){
    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
      t() %>% colMeans()
    x %>% dplyr::select(-values) %>%
      pivot_wider(names_from = "representator", values_from = "rank")
  }) %>%
  unnest("values")

representators <- c("error", "ts", "error.features", "ts.features", "forecast")

## in most cases, error is the best
representator_summarise %>% rowwise() %>%
  mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
  pull(min) %>%
  table()

## only in one case, error is the worst
representator_summarise %>% rowwise() %>%
  mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
  pull(max) %>%
  table()
mcb(representator_summarise %>% dplyr::select(all_of(representators)))

# no hierarchy
rank(store_all$rank)[which(store_all$cluster == "")]

# natural hierarchy
rank(store_all$rank)[which(store_all$cluster == "natural")]

@@

### cluster rank
```{r}
# cluster rank
cluster_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(cluster, values, rank)) %>%
  mutate_at("values", purrr::map, function(x){
    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
      t() %>% colMeans() %>% rank()
    x %>% dplyr::select(-values) %>%
      pivot_wider(names_from = "cluster", values_from = "rank")
  }) %>%
  unnest("values")

cluster_summarise %>% dplyr::select(-c(representator, distance)) %>%
  mcb()

@@

```{r}
distance_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(distance, values, rank)) %>%
  mutate_at("values", purrr::map, function(x){
    x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
      t() %>% colMeans() %>% rank()
    x %>% select(-values) %>%
      pivot_wider(names_from = "distance", values_from = "rank")
  }) %>%
  unnest("values")
distance_summarise %>% select(-c(representator, cluster)) %>%
  mcb()

distances <- c("euclidean", "dtw", "negcor", "cor", "uncorrelation")
distance_summarise %>% rowwise() %>%
  mutate(max = distances[which.max(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
  pull(max) %>%
  table()
distance_summarise %>% rowwise() %>%
  mutate(min = distances[which.min(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
  pull(min) %>%
  table()
```

>>>>

```{r, include=FALSE, echo=FALSE}

set.seed(1065)
S <- rbind(c(1,1,1), c(0, 1, 1), diag(3))

@@

```{r, echo=FALSE, message=FALSE}
source("illurstrative.R")
```

@@

$$
\begin{bmatrix}
e_{C,t} \\ e_{D,t} \\ e_{E,t}
\end{bmatrix} = \begin{bmatrix}
0 & 0 & 0 \\
0 & 0.4 & x \\
0 & x & 0.4
\end{bmatrix} \begin{bmatrix}
e_{C,t-1} \\ e_{D,t-1} \\ e_{E,t-1}
\end{bmatrix} + \begin{bmatrix}
\varepsilon_{C,t} \\ \varepsilon_{D,t} \\ \varepsilon_{E,t}
\end{bmatrix}
$$
$$
\begin{bmatrix}
y_{C,t} \\ y_{D,t} \\ y_{E,t}
\end{bmatrix} = \begin{bmatrix}
0 \\
0.05 \\
0.045
\end{bmatrix} t + \begin{bmatrix}
e_{C,t} \\ e_{D,t} \\ e_{E,t}
\end{bmatrix}
$$

$\boldsymbol{\varepsilon}_t$ are white noises.

```{r}
r1 <- step2(c(0.3, 0.3))
r1 %>% mutate(mint = mint/base, mint2 = mint2/base) %>% group_by(names) %>% summarise_at(c("mint", "mint2"), mean)

r2 <- step2(c(0, 0))
r2 %>% mutate(mint = mint/base, mint2 = mint2/base) %>% group_by(names) %>% summarise_at(c("mint", "mint2"), mean)

r3 <- step2(c(-0.3, -0.4))
#r3 %>% group_by(names) %>% summarise_at(c("base", "mint", "mint2"), mean)
r3 %>% mutate(mint = mint/base, mint2 = mint2/base) %>% group_by(names) %>% summarise_at(c("mint", "mint2"), mean)

@@

```{r, include=FALSE}

which.best <- function(x){
  names(x$means)[1]
}

is.bestsignificant <- function(x){
  x$mean[1] + x$cd/2 < x$mean[2] - x$cd/2
}

which.worst <- function(x){
  names(x$means)[length(x$means)]
}

is.worstsignificant <- function(x){
  x$mean[1] + x$cd/2 < x$mean[x$k] - x$cd/2
}

tmp_mcb <- function(x){
  a <- do.call(cbind, x$values)
  colnames(a) <- x$representator
  tsutils::nemenyi(a, plottype = "vmcb")
}
```

```{r}
# representator rank
representator_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(representator, values, rank)) %>%
  mutate(orig_values = values) %>%
  mutate_at("values", purrr::map, function(x){

    a <- do.call(cbind, x$values)
    colnames(a) <- x$representator
    tsutils::nemenyi(a, plottype = "none")
  })

representator_summarise <- representator_summarise %>%
  rowwise() %>% mutate(best = which.best(values),
                       sigbest = is.bestsignificant(values),
                       worst = which.worst(values),
                       sigworst = is.worstsignificant(values))

representors <- c("ts", "error", "ts.features", "error.features", "forecast")
for (method in representors) {
  print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
                NROW(representator_summarise %>% filter(best == method)),
                method,
                NROW(representator_summarise %>% filter(best == method, sigbest)),
                NROW(representator_summarise %>% filter(worst == method)),
                NROW(representator_summarise %>% filter(worst == method, sigworst))))
}
```

```{r}

# representators <- c("error", "ts", "error.features", "ts.features", "forecast")
#
# ## in most cases, error is the best
# representator_summarise %>% rowwise() %>%
#   mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
#   pull(min) %>%
#   table()
#
# ## only in one case, error is the worst
# representator_summarise %>% rowwise() %>%
#   mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
#   pull(max) %>%
#   table()
# mcb(representator_summarise %>% select(representators))

@@

### cluster rank
```{r}
# cluster rank
cluster_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(cluster, values, rank)) %>%
  mutate(orig_values = values) %>%
  mutate_at("values", purrr::map, function(x){
    a <- do.call(cbind, x$values)
    colnames(a) <- x$cluster
    tsutils::nemenyi(a, plottype = "none")
  }) %>% rowwise() %>% mutate(best = which.best(values),
                       sigbest = is.bestsignificant(values),
                       worst = which.worst(values),
                       sigworst = is.worstsignificant(values))

cluster_summarise
# cluster_summarise %>% select(-c(representator, distance)) %>%
#   mcb()

@@

```{r}

distance_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(distance, values, rank)) %>%
  mutate(orig_values = values) %>%
  mutate_at("values", purrr::map, function(x){
    a <- do.call(cbind, x$values)
    colnames(a) <- x$distance
    tsutils::nemenyi(a, plottype = "none")
  }) %>% rowwise() %>% mutate(best = which.best(values),
                       sigbest = is.bestsignificant(values),
                       worst = which.worst(values),
                       sigworst = is.worstsignificant(values))

distance_summarise

# distance_summarise <- store_all %>% filter(distance != "") %>%
#   nest(values = c(distance, values, rank)) %>%
#   mutate_at("values", purrr::map, function(x){
#     x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
#       t() %>% colMeans() %>% rank()
#     x %>% select(-values) %>%
#       pivot_wider(names_from = "distance", values_from = "rank")
#   }) %>%
#   unnest("values")
# distance_summarise %>% select(-c(representator, cluster)) %>%
#   mcb()
#
# distances <- c("euclidean", "dtw", "negcor", "cor", "uncorrelation")
# distance_summarise %>% rowwise() %>%
#   mutate(max = distances[which.max(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
#   pull(max) %>%
#   table()
# distance_summarise %>% rowwise() %>%
#   mutate(min = distances[which.min(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
#   pull(min) %>%
#   table()
```

```{r}
distances <- c("cor", "dtw", "euclidean", "negcor", "uncorrelation")
for (method in distances) {
  print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
                NROW(distance_summarise %>% filter(best == method)),
                method,
                NROW(distance_summarise %>% filter(best == method, sigbest)),
                NROW(distance_summarise %>% filter(worst == method)),
                NROW(distance_summarise %>% filter(worst == method, sigworst))))
}
```

@@

```{r}
# representator rank
representator_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(representator, values, rank)) %>%
  mutate(orig_values = values) %>%
  mutate_at("values", purrr::map, function(x){

    a <- do.call(cbind, x$values)
    colnames(a) <- x$representator
    tsutils::nemenyi(a, plottype = "none")
  })

representator_summarise <- representator_summarise %>%
  rowwise() %>% mutate(best = which.best(values),
                       sigbest = is.bestsignificant(values),
                       worst = which.worst(values),
                       sigworst = is.worstsignificant(values))

representors <- c("ts", "error", "ts.features", "error.features", "forecast")
for (method in representors) {
  print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
                NROW(representator_summarise %>% filter(best == method)),
                method,
                NROW(representator_summarise %>% filter(best == method, sigbest)),
                NROW(representator_summarise %>% filter(worst == method)),
                NROW(representator_summarise %>% filter(worst == method, sigworst))))
}
```

```{r}

# representators <- c("error", "ts", "error.features", "ts.features", "forecast")
#
# ## in most cases, error is the best
# representator_summarise %>% rowwise() %>%
#   mutate(min = representators[which.min(c(error, ts, error.features, ts.features, forecast))]) %>%
#   pull(min) %>%
#   table()
#
# ## only in one case, error is the worst
# representator_summarise %>% rowwise() %>%
#   mutate(max = representators[which.max(c(error, ts, error.features, ts.features, forecast))]) %>%
#   pull(max) %>%
#   table()
# mcb(representator_summarise %>% select(representators))

# no hierarchy is not good: 391 / 428
print(sprintf("rank of no clustering: %s", rank(store_all$rank)[1]))

# natural hierarchy is not bad: 72/428
print(sprintf("rank of natural hierarchy: %s", rank(store_all$rank)[2]))

@@

### cluster rank
```{r}
# cluster rank
cluster_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(cluster, values, rank)) %>%
  mutate(orig_values = values) %>%
  mutate_at("values", purrr::map, function(x){
    a <- do.call(cbind, x$values)
    colnames(a) <- x$cluster
    tsutils::nemenyi(a, plottype = "none")
  }) %>% rowwise() %>% mutate(best = which.best(values),
                       sigbest = is.bestsignificant(values),
                       worst = which.worst(values),
                       sigworst = is.worstsignificant(values))

cluster_summarise
# cluster_summarise %>% select(-c(representator, distance)) %>%
#   mcb()

@@

```{r}

distance_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(distance, values, rank)) %>%
  mutate(orig_values = values) %>%
  mutate_at("values", purrr::map, function(x){
    a <- do.call(cbind, x$values)
    colnames(a) <- x$distance
    tsutils::nemenyi(a, plottype = "none")
  }) %>% rowwise() %>% mutate(best = which.best(values),
                       sigbest = is.bestsignificant(values),
                       worst = which.worst(values),
                       sigworst = is.worstsignificant(values))

distance_summarise

# distance_summarise <- store_all %>% filter(distance != "") %>%
#   nest(values = c(distance, values, rank)) %>%
#   mutate_at("values", purrr::map, function(x){
#     x$rank <- do.call(cbind, x$values) %>% apply(1, rank) %>%
#       t() %>% colMeans() %>% rank()
#     x %>% select(-values) %>%
#       pivot_wider(names_from = "distance", values_from = "rank")
#   }) %>%
#   unnest("values")
# distance_summarise %>% select(-c(representator, cluster)) %>%
#   mcb()
#
# distances <- c("euclidean", "dtw", "negcor", "cor", "uncorrelation")
# distance_summarise %>% rowwise() %>%
#   mutate(max = distances[which.max(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
#   pull(max) %>%
#   table()
# distance_summarise %>% rowwise() %>%
#   mutate(min = distances[which.min(c(euclidean, dtw, negcor, cor, uncorrelation))]) %>%
#   pull(min) %>%
#   table()
```

```{r}
distances <- c("cor", "dtw", "euclidean", "negcor", "uncorrelation")
for (method in distances) {
  print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
                NROW(distance_summarise %>% filter(best == method)),
                method,
                NROW(distance_summarise %>% filter(best == method, sigbest)),
                NROW(distance_summarise %>% filter(worst == method)),
                NROW(distance_summarise %>% filter(worst == method, sigworst))))
}
```

## Prison

```{r, include=FALSE, echo=FALSE}
store_all <- NULL
for (batch in 0:7) {
  store_all <- readRDS(paste0("prison/store_", batch, ".rds"))$output %>%
    output_pre() %>% mutate(batch = batch) %>%
    filter(rf_method == .env$rf_method, accuracy_method == .env$accuracy_method) %>%
    dplyr::select(-rf_method, -accuracy_method) %>%
    rbind(store_all)
}

```{r}
mcb(store_mat)
```
For prison data, all the methods are insignificantly different.
```{r}
store_all %>% arrange(rank)
```

```{r}
# representator rank
representator_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(representator, values, rank)) %>%
  mutate(orig_values = values) %>%
  mutate_at("values", purrr::map, function(x){

    a <- do.call(cbind, x$values)
    colnames(a) <- x$representator
    tsutils::nemenyi(a, plottype = "none")
  })

representator_summarise <- representator_summarise %>%
  rowwise() %>% mutate(best = which.best(values),
                       sigbest = is.bestsignificant(values),
                       worst = which.worst(values),
                       sigworst = is.worstsignificant(values))

representors <- c("ts", "error", "ts.features", "error.features", "forecast")
for (method in representors) {
  print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
                NROW(representator_summarise %>% filter(best == method)),
                method,
                NROW(representator_summarise %>% filter(best == method, sigbest)),
                NROW(representator_summarise %>% filter(worst == method)),
                NROW(representator_summarise %>% filter(worst == method, sigworst))))
}
```

```{r}
# no hierarchy is not good: 391 / 428
print(sprintf("rank of no clustering: %s", rank(store_all$rank)[1]))

# natural hierarchy is not bad: 72/428
print(sprintf("rank of natural hierarchy: %s", rank(store_all$rank)[2]))

tmp <- store_all %>% filter(distance == "")
tmp$rank <- do.call(cbind, tmp$values) %>% apply(1, rank) %>%
  t() %>% colMeans()
```

### cluster rank
```{r}
# cluster rank
cluster_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(cluster, values, rank)) %>%
  mutate(orig_values = values) %>%
  mutate_at("values", purrr::map, function(x){
    a <- do.call(cbind, x$values)
    colnames(a) <- x$cluster
    tsutils::nemenyi(a, plottype = "none")
  }) %>% rowwise() %>% mutate(best = which.best(values),
                       sigbest = is.bestsignificant(values),
                       worst = which.worst(values),
                       sigworst = is.worstsignificant(values))

cluster_summarise
```

```{r}

distance_summarise <- store_all %>% filter(distance != "") %>%
  nest(values = c(distance, values, rank)) %>%
  mutate(orig_values = values) %>%
  mutate_at("values", purrr::map, function(x){
    a <- do.call(cbind, x$values)
    colnames(a) <- x$distance
    tsutils::nemenyi(a, plottype = "none")
  }) %>% rowwise() %>% mutate(best = which.best(values),
                       sigbest = is.bestsignificant(values),
                       worst = which.worst(values),
                       sigworst = is.worstsignificant(values))

distance_summarise
```

```{r}
distances <- c("cor", "dtw", "euclidean", "negcor", "uncorrelation")
for (method in distances) {
  print(sprintf("In %s cases, %s is the best, where %s is significantly best. In %s cases, it is the worst, where %s is significantly worse than the best one.",
                NROW(distance_summarise %>% filter(best == method)),
                method,
                NROW(distance_summarise %>% filter(best == method, sigbest)),
                NROW(distance_summarise %>% filter(worst == method)),
                NROW(distance_summarise %>% filter(worst == method, sigworst))))
}
```
